A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-24 journal/abstract.tex
related

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  A simple operator-selection approach to reducing the number of mutants can reduce the cost of our approach by 70\%, while producing a gain in fault identification accuracy.  We additionally show that our approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  A simple operator-selection approach to reducing the number of mutants can reduce the cost of our approach by 70\%, while producing a gain in fault identification accuracy.  We additionally show that our approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs, and can help triage crashes found in fuzzing of non-compiler programs more effectively than a state-of-the-art technique.

### 2019-09-24 journal/experiments.tex
related

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming (from Chen et al.'s PLDI 2013 paper \cite{PLDI13}), which we hereafter refer to as the FPF benchmark.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  In fact, on examination, only two of the 11 crash bugs are not distinguished by simply examining the crash message.  Faults that produce a crash are also likely to be much easier to debug than semantic problems such as all of the GCC wrong code bugs and most of the JavaScript faults --- e.g., following a dynamic slice might well suffice.

@@

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our metrics.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.  This is only a moderately strong oracle, and allows serious deviations from both the JavaScript language specification and normal SpiderMonkey behavior, while checking some complex details, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely --- only missed optimizations are allowed.

@@

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault --- a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes, but effectively disabled the mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (\% of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

No method performs extremely well --- for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in the first 25-30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

For GCC wrong code faults, the baseline chance that two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric showed the same fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity was 79.4\% (median 100\%).

Slicing the GCC tests into 20 random equal-sized test subsets and comparing with function and line coverage metrics (Figure \ref{comparegcc}) we find that differences in APFD values are statistically significant between our metric and both benchmark metrics, by Wilcoxon test, with $p < 0.0005$, and the mean APFD improvement --- even for only 55 tests, exposing only 6-11 faults (mean of 7.75 faults) --- is more than 3.8\% better than either benchmark metric.

@@

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  This is basically a trade-off.  MUSE, MUSEUM, and Metallaxis-FL provide localization for many more faults, in a more diverse range of settings (with single failing tests, no repairs, etc.), and using more diverse information --- but, in cases where {\bf Repair} provides a localization, it seems to often be higher quality due to its restriction to a high-signal source of information (mutants repairing failing tests, only).  In settings, unlike compilers, where there are relatively few repairs, {\bf Repair} also produces very little incorrect information, and so has a low cost to the user in terms of wasted attention.  Note that our heuristic to stop reading after 5 wrong localizations is not even needed for all but one CoREBench fault --- {\bf Repair} suggests 1-3 statements at most.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply, without any loss of ability to identify or localize faults.

@@

The largest threat to validity is that this paper's core conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into our results.  In order to make it possible to check for these problems, we have made the raw data for a re-analysis available: \url{https://github.com/agroce/mutants16/tree/master/tests}.  The data required for analysis of the non-compiler faults is available from the authors of the respective studies (see the acknowledgements at the end of the paper).

>>>>

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming (from Chen et al.'s PLDI 2013 paper \cite{PLDI13}), which we hereafter refer to as the FPF benchmark.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  In fact, on examination, only two of the 11 crash bugs are not distinguished by simply examining the crash message.  Faults that produce a crash are also likely to be much easier to debug than semantic problems such as all of the GCC wrong code bugs and most of the JavaScript faults-- e.g., following a dynamic slice might well suffice.

@@

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our metrics.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.  This is only a moderately strong oracle, and allows serious deviations from both the JavaScript language specification and normal SpiderMonkey behavior, while checking some complex details, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely---only missed optimizations are allowed.

@@

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault---a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes, but effectively disabled the mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (\% of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

No method performs extremely well---for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in the first 25-30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

For GCC wrong code faults, the baseline chance that two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric showed the same fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations---essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity was 79.4\% (median 100\%).

Slicing the GCC tests into 20 random equal-sized test subsets and comparing with function and line coverage metrics (Figure \ref{comparegcc}) we find that differences in APFD values are statistically significant between our metric and both benchmark metrics, by Wilcoxon test, with $p < 0.0005$, and the mean APFD improvement---even for only 55 tests, exposing only 6-11 faults (mean of 7.75 faults)---is more than 3.8\% better than either benchmark metric.

@@

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  This is basically a trade-off.  MUSE, MUSEUM, and Metallaxis-FL provide localization for many more faults, in a more diverse range of settings (with single failing tests, no repairs, etc.), and using more diverse information---but, in cases where {\bf Repair} provides a localization, it seems to often be higher quality due to its restriction to a high-signal source of information (mutants repairing failing tests, only).  In settings, unlike compilers, where there are relatively few repairs, {\bf Repair} also produces very little incorrect information, and so has a low cost to the user in terms of wasted attention.  Note that our heuristic to stop reading after 5 wrong localizations is not even needed for all but one CoREBench fault---{\bf Repair} suggests 1-3 statements at most.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable---almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply, without any loss of ability to identify or localize faults.

@@

The largest threat to validity is that this paper's core conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into our results.  In order to make it possible to check for these problems, we have made the raw data for a re-analysis of the PLDI13 benchmark available, including the tests, ground truth, and mutants, at \url{https://github.com/agroce/compilermutants}; the fuzzgoat example is also available, including source code for a simple version of our FPF algorithms, at \url{https://github.com/agroce/fuzzgoattriage}.  The data required for analysis of the non-compiler faults is available from the authors of the respective studies (see the acknowledgements at the end of the paper).
